Scholten Read Sanborn

### 2015-11-18 shinyapps/scholtenReadSanborn2014.Rmd
start writing paper for SSRM

---
title: "Scholten Read Sanborn"
author: "Daniel Wall"
date: "November 12, 2015"
output: html_document
runtime: shiny
---

@@

## Exponential Discounting

@@

## The interval discounting model: A hybrid evaluation rule

@@

## Tradeoff model

>>>>

---
title: "Scholten Read Sanborn"
author: "Daniel Wall"
date: "November 12, 2015"
output: 
  html_document: 
    number_sections: yes
    toc: yes
runtime: shiny
---

@@

# Exponential Discounting

@@

# The interval discounting model: A hybrid evaluation rule

@@

# Tradeoff model
